Constructive Preference Elicitation by Setwise Max-margin Learning

### 2016-01-11 paper/ijcai16.tex
paper: add rough sketch of the experimental section.

\section{Experiments}

@@

@@

\paragraph{Synthetic Dataset.} As a first test, we evaluated the performance
of the three methods on a synthetic dataset, where all configurations

We ran all methods on $20$ different users. The hidden, true weight vectors
were the same for all three methods.

@@

\stefano{what about an experiment with Horn constraints?}

\paragraph{Constructive Dataset.} \stefano{WRITEME}

@@

>>>>

\section{Experiments}
\label{sec:experiments}

@@

\stefano{describe the baselines}

We implemented the {\sc SetMargin} algorithm using Python, while the MILP
problems were solved with Gurobi 6.5.0. The full source of the experiments is
available at \stefano{add URL}.

@@

\paragraph{Synthetic Dataset.} In order to evaluate the convergence and
scalability properties of the proposed method, following~\cite{guo2010real} and
\cite{viappiani2010optimal}, we evaluated it on a number of increasingly larger
synthetic datasets. More specifically, we defined $7$ synthetic dataset over
$n=2,\ldots,7$ attributes, with each attribute taking one of $n$ possible
values.
In other words, for $n=2$ we have that the feasible space
$\calX_\text{feasible}$ is $[2] \times [2]$, while for $n=3$ we have
$\calX_\text{feasible} = [3] \times [3] \times [3]$, and so on.
The cardinality of $\calX_\text{feasible}$ is $n^n$, and grows
(super-)exponentially with $n$. For $n=3$, the dataset is comparable to
the synthetic ones used in~\cite{guo2010real} and~\cite{viappiani2010optimal},
while for larger $n$ it grows much larger than those typically used in the
Bayesian preference elicitation literature, and as such represents a good
test bed for evaluating the scalability of the various methods.

In order to work, the competitors require the dataset to represented
explicitly, so we had to ground the $7$ datasets. This is not the case for {\sc
SetMargin}, in which case the set of feasible configurations
$\calX_\text{feasible}$ can be encoded {\em implicitly} through simple linear
integer constraints. All of the methods can deal with binary vectors only; we
translated the integer-valued configurations to such format using a simple
one-hot encoding. For {\sc SetMargin}, this requires to encode additional
XOR constraints. \stefano{explain}

The three methods were evaluated on user weight vectors sampled from two
distinct distributions: a normal distribution with mean $25$ and
variance $\frac{25}{3}$, and from a uniform distribution over $[0,
100]$. This procedure mimics closely~\cite{guo2010real}. In order to assess our
method in a truly sparse setting, we obtained a set of sparse normal and
uniform weight vectors by randomly deleting $80\%$ of the non-zero entries from
the already sampled vectors. We name the four settings {\sc normal}, {\sc
uniform}, {\sc sparse\_normal} and {\sc sparse\_uniform}. We sampled a total
of $100$ weight vectors for each setting. The three methods were evaluated
on the very same weight vectors.

@@

\paragraph{Constructive Dataset.} Next, we tested {\sc SetMargin} on a truly
constructive setting, which can not be readily handled by non-constructive
methods.

@@

The configurations constraints:
%
$$ x_i \Leftarrow x_{j_1} \lor \ldots \lor x_{j_n} $$
%
have been translated into MILP constraints of the form:
%
$$ (1 - x_i) + x_{j_1} + \ldots + x_{j_n} \ge 1 $$
